A Comparison of Graph Processing Systems

### 2020-08-28 documentation/paper/sections/testingMethods.tex
erste fixes der Rückmeldung

\subsection{Hardware and Software}
For testing all systems we used 5 machines with 96 CPU cores each (48 physical) and 256 GB of RAM. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All five machines were running Ubuntu 18.04.2 LTS.
Setup of each framework was performed according to our provided installation guides\footnote{The setup guides are available at \url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}.

All benchmarks were initiated by our benchmark script that is available in our repository. Galois, Gemini and Giraph were benchmarked on both the 5-node cluster and a singe machine.
Since Galois supports this parameter, we ran multiple tests comparing Galois' performance with different thread counts on a single machine.

The complete benchmark log files and extracted raw results will be available in our repository as well.

@@

\subsection{Graphs}
The graphs used in our testing can be seen in detail in \autoref{tbl:graphs}. We included a variaty of different graph sizes, from relatively small graphs like the flickr graph up to an rMat28 with $4.2$ billion edges. All graphs except the rMat27 and rMat28 are exemplary real-world graphs and were retrieved from the graph database\footnote{\url{http://konect.uni-koblenz.de/}} associated with the Koblenz Network Collection (KONECT)\cite{konect}.
Both the rMat27 and rMat28 were created with a modified version (we changed the output format to EdgeList) of a graph generator provided by Ligra.
\begin{table}
	\centering
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
	\caption{Size comparison of the used graphs}
	\label{tbl:graphs}
\end{table}

@@

\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
TODO
	\centering
	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&\\
		SSSP&?, Push, Pull&&&&\\
		BFS&Yes&&*&&\\
		\hline
	\end{tabularx}
	\caption{Tested algorithms of the frameworks}
	\label{tbl:algorithms}

	* Algorithm not natively supported

>>>>

\subsection{Hardware}
For testing the graph processing systems, we used 5 machines with two AMD EPYC 7401 (24-Cores) and 256 GB of RAM each. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All five machines were running Ubuntu 18.04.2 LTS.
Setup of each framework was performed according to our provided installation guides\footnote{The setup guides are available at \url{https://github.com/SerenGTI/Forschungsprojekt/tree/master/documentation}}.

\subsection{Benchmark Software}
All benchmarks were initiated by our benchmark script, that is available in our repository. Galois, Gemini and Giraph were benchmarked on both the 5-node cluster and a singe machine.
Since Galois supports this parameter, we ran multiple tests comparing Galois' performance with different thread counts on a single machine.

The complete benchmark log files and extracted raw results are available in our repository.

\subsection{Data Sets}
The graphs used in our testing can be seen in detail in \autoref{tbl:graphs}. We included a variaty of different graph sizes, from relatively small graphs like the flickr graph with 100 thousand edges up to an rMat28 with $4.2$ billion edges. All graphs except the rMat27 and rMat28 are exemplary real-world graphs and were retrieved from the graph database\footnote{\url{http://konect.uni-koblenz.de/}} associated with the Koblenz Network Collection (KONECT)\cite{konect}.
Both the rMat27 and rMat28 were created with a modified version (we changed the output format to EdgeList) of a graph generator provided by Ligra.
\begin{table}
	\centering
	\caption{Size Comparison of the Used Graphs}
	\begin{tabular}{crr}
		\hline
		\bf{Graph}&\# Vertices (M)&\# Edges (M)\\\hline
		flickr&    		0.1&  2\\
		orkut&          3&    117\\
		wikipedia&      12&   378\\
		twitter&     	52&   1963\\
		rMat27&         63&   2147\\
		friendster&     68&   2586\\
		rMat28&         121&  4294\\
		\hline
	\end{tabular}
	\label{tbl:graphs}
\end{table}

@@

@@

\newcommand{\txtdag}{\textsuperscript{\textdagger}}
\begin{table}
	\renewcommand{\arraystretch}{1.3}
	\centering
	\caption{Tested Algorithms of Each Framework}
	\begin{tabularx}{0.9\columnwidth}{cYYYYY}
		\bf{Algorithm}&Galois&Gemini&Giraph&Ligra&Polymer\\\hline
		PageRank&$\Delta$Push, $\Delta$Pull&&&&Regular, $\Delta$\\\hline
		SSSP&?, Push, Pull&&&&\\\hline
		BFS&Yes&&Yes*&&\\
		\hline
	\end{tabularx}
	\label{tbl:algorithms}

	{\vspace*{1ex}* Algorithm not natively supported

	\txtdag{} Modified algorithm

	\textsuperscript{d} Single node and distributed
	}
